\pkg{Rgbp}: Bayesian Hierarchical Modeling and Frequentist Method Check

### 2013-04-12 jss/article.tex
what changes?

\subsection{Pseudo-data Generation Process}
Figure 1 will be helpful to understand this process. As we can see in (8), the distribution of each true parameter ($p_{j},~j=1,\ldots, 18$) depends on two hyper-parameters, $r$ and $\beta_{(m\times1)}$, where $m$ is the number of regression coefficients. Once we fix these hyper-parameters at specific values, we can generate true parameters. Suppose we sampled 500 $\textbf{p}_{(18\times1)}$'s, \emph{i.e.}, $\{\textbf{p}^{(i)}_{(18\times1)},~i=1, \ldots, 500\}$. Then, we can also generate $\{\textbf{z}^{(i)}_{(18\times1)},~i=1, \ldots, 500\}$ given each $p_{ij},$ where $i$ indicates $i$-th pseudo-dataset and $j$ does $j$-th player. Next, \code{coverage} fits the Binomial hierarchical model 500 times on $\{(\textbf{z}^{(i)}_{(18\times1)}, \textbf{n}_{(18 \times 1)}),~i=1, \ldots, 500\}$ to obtain 500*18 interval estimates. Taking the first player as an example, we have 500 pairs of ($z_{i1}$, $p_{i1}$), $j=1,\ldots, 500$, and 500 interval estimates.
\begin{figure}[h]
\begin{center}
\includegraphics[width=5cm]{process.png}
\caption{Pseudo-data generating process}
\end{center}
\end{figure}

\subsection{Unbiased Coverage Probability}
Based on the generated pseudo-datasets, let's define an indicator variable, $I_{ij}$, which is 1 if $j$-th interval estimate from $i$-th pseudo-dataset includes $p_{ij}$ and 0 otherwise. One way to estimate the coverage probability is taking average over these indicator variables. We call it an unbiased coverage probability estimate. For example, $\bar{I}_{1}=\sum_{i=1}^{500}I_{i1}/500$ is the estimated coverage probability for the first player.
\subsection{Rao-Blackwellized Coverage Probability}
Based on the definition of Rao-Blackwellization, we define $E(I_{ij}\vert z_{ij}, r, \beta$) as the Rao-Blackwellized coverage probability, where $r$ and $\beta$ were fixed at first (see 5.1). This expectation is the same as P$(\hat{p}_{ij, low}\le p_{ij} \le\hat{p}_{ij, upp}\vert z_{ij}, r, \beta)$, where $\hat{p}_{ij, low}$ and $\hat{p}_{ij, upp}$ are interval estimates (numeric values). We can calculated this probability exactly because we know the distribution of $(p_{ij} \vert z_{ij}, r, \beta)$ in (9). Then, we can estimate the first player's coverage probability by Rao-Blackwellized coverage probability, for instance, $\sum_{i=1}^{500}E(I_{i1}\vert z_{i1}, r, \beta)/500$.
\section[Example]{Example}
\subsection[Known Prior Mean]{Known Prior Mean}
Using 10 hospital data with PR
\subsection[Unknown Prior Mean and No Covariate]{Unknown Prior Mean and No Covariate}
Using 8 school data with GR
\subsection[Unknown Prior Mean and One Covariate]{Unknown Prior Mean and One Covariate}
Using 18 baseball data with BR

>>>>

\subsection{Pseudo-data Generation Process}
Figure 1 will be helpful to understand this process. As we can see in (8), the distribution of each true parameter ($p_{j},~j=1,\ldots, 18$) depends on two hyper-parameters, $r$ and $\beta_{(m\times1)}$, where $m$ is the number of regression coefficients. Once we fix these hyper-parameters at specific values, we can generate true parameters. Suppose we sampled 500 $\textbf{p}_{(18\times1)}$'s, \emph{i.e.}, $\{\textbf{p}^{(i)}_{(18\times1)},~i=1, \ldots, 500\}$. Then, we can also generate $\{\textbf{z}^{(i)}_{(18\times1)},~i=1, \ldots, 500\}$ given each $p_{ij},$ where $i$ indicates $i$-th pseudo-dataset and $j$ does $j$-th player. Next, \code{coverage} fits the Binomial hierarchical model 500 times on $\{(\textbf{z}^{(i)}_{(18\times1)}, \textbf{n}_{(18 \times 1)}),~i=1, \ldots, 500\}$ to obtain 500*18 interval estimates. Taking the first player as an example, we have 500 pairs of ($z_{i1}$, $p_{i1}$), $i=1,\ldots, 500$, and 500 interval estimates.
\begin{figure}[h]
\begin{center}
\includegraphics[width=5cm]{process.png}
\caption{Pseudo-data generating process}
\end{center}
\end{figure}

\subsection{Unbiased Coverage Probability}
Based on the generated pseudo-datasets, let's define an indicator variable, $I_{ij}$, which is 1 if $j$-th player's interval estimate from $i$-th pseudo-dataset includes $p_{ij}$ and 0 otherwise. One way to estimate the coverage probability is taking average over these indicator variables. We call it an unbiased coverage probability estimate. For example, $\bar{I}_{1}=\sum_{i=1}^{500}I_{i1}/500$ is the estimated coverage probability for the first player.

\subsection{Rao-Blackwellized Coverage Probability}
Based on the definition of Rao-Blackwellization, we define $E(I_{ij}\vert z_{ij}, r, \beta$), where $r$ and $\beta$ were fixed at first (see 5.1) and $z_{ij}$ is a sufficient statistic. This expectation is the same as Pr$(\hat{p}_{ij, low}\le p_{ij} \le\hat{p}_{ij, upp}\vert z_{ij}, r, \beta)$, where ($\hat{p}_{ij, low}$, $\hat{p}_{ij, upp}$) is $j$-th player's interval estimates (numeric values) on the $i$-th dataset. We can calculated this probability exactly because we know the distribution of $(p_{ij} \vert z_{ij}, r, \beta)$ in (9). Then, we can estimate the first player's coverage probability, for instance, by $\sum_{i=1}^{500}E(I_{i1}\vert z_{i1}, r, \beta)/500$.
\section[Example]{Example}
\subsection[Known Prior Mean]{Known Prior Mean}
Using 10 hospital data with PR
\subsection[Unknown Prior Mean and No Covariate]{Unknown Prior Mean and No Covariate}
Using 8 school data with GR
\subsection[Unknown Prior Mean and One Covariate]{Unknown Prior Mean and One Covariate}
Using 18 baseball data with BR
